The first high-redshift Changing Look Quasars

### 2019-11-07 tex/other_tex/201909/CIV_notes_20190917v2.tex
CIV tex/ tidy up

I also don’t think this is a recombination (for H, He) vs. collisionally excited lines (MgII, C IV etc.) thing, though I’m not sure.

@@

\citet{Coatman2016} show that %%Black hole masses are crucial to understanding the physics of the connection between quasars and their host galaxies and measuring cosmic black hole-growth. 
at high redshift, $z>2.1$, black hole masses are normally derived using the velocity width of the C IV λλ1548, 1550 broad emission line, based on the assumption that the observed velocity widths arise from virial- induced motions. In many quasars, the C IV emission line exhibits significant blue asymmetries (‘blueshifts’) with the line centroid displaced by up to thousands of km s−1 to the blue. These blueshifts almost certainly signal the presence of strong outflows, most likely originating in a disc wind. We have obtained near-infrared spectra, including the Hα λ6565 emission line, for 19 luminous (LBol = 46.5–47.5 erg s−1) Sloan Digital Sky Survey quasars, at redshifts 2 < z < 2.7, with C IV emission lines spanning the full range of blueshifts present in the population. A strong correlation between C IV velocity width and blueshift is found and, at large blueshifts, >2000kms−1, the velocity widths appear to be dominated by non-virial motions. Black hole masses, based on the full width at half-maximum of the C IV emission line, can be overestimated by a factor of 5 at large blueshifts. A larger sample of quasar spectra with both C IV and H β, or Hα, emission lines will allow quantitative corrections to C IV-based black hole masses as a function of blueshift to be derived. We find that quasars with large C IV blueshifts possess high Eddington luminosity ratios and that the fraction of high-blueshift quasars in a flux-limited sample is enhanced by a factor of approximately 4 relative to a sample limited by black hole mass.

@@

%% Romain A. Meyer, Sarah E. I. Bosman, Richard S. Ellis  https://arxiv.org/abs/1902.04558v1
\citet{Meyer2019} present the results of a model-independent investigation of the rest-frame UV spectra from a comprehensive sample of 394 quasars in the redshift range $1.5\leq z \leq 7.5$. We fit the main Broad Emission Lines (BELs) in the rest-frame range 1280 \AA $\leq \lambda \leq $3000 \AA (O I, C II, Si IV, C III, C IV and Mg II) with a lightly-supervised spline fitting technique. Redshifts are derived from the peaks of each fitted BEL and used to compute relative velocity shifts. We show that our method gives unbiased velocity shifts and is insensitive to spectral resolution and instrumental parameters. It is found that the average blueshift of the \civ\, line with respect to several low-ionisation lines in luminosity-matched samples does not significantly evolve over $1.5\leq z\leq 6$. However, the average blueshift increases significantly by a factor $\sim$2.5 at $z \geq 6$. We propose that this redshift evolution can be explained by \civ\, winds launched perpendicularly to an accretion disk with increased torus opacity at high-redshift, coupled with a potential orientation-driven selection bias. Our results open new exciting avenues of investigation into young quasars in the reionisation epoch.

@@

@@

\subsection{Multi-wavelength properties}
MIR \\
Radio \\

>>>>

Recombination (e.g. H, He) vs. collisionally excited lines (\mgii, \civ).

@@

\citet{Coatman2016} show that at high redshift, $z>2.1$, black hole
masses are normally derived using the velocity width of the C IV
$\lambda \lambda$1548, 1550 broad emission line, based on the
assumption that the observed velocity widths arise from virial-
induced motions. In many quasars, the \civ emission line exhibits
significant blue asymmetries  with the line centroid
displaced by up to thousands of km s$^{-1}$ to the blue. These blueshifts
almost certainly signal the presence of strong outflows, most likely
originating in a disc wind. We have obtained near-infrared spectra,
including the H$\alpha$ $\lambda$6565 emission line, for 19 luminous 
(L$_{\rm Bol} =46.5–47.5$ erg s$^{-1}$) Sloan Digital Sky Survey quasars, at redshifts $2 <
z < 2.7$, with \civ emission lines spanning the full range of
blueshifts present in the population. A strong correlation between C
IV velocity width and blueshift is found and, at large blueshifts,
$>$2000 km s$−1$, the velocity widths appear to be dominated by non-virial
motions. Black hole masses, based on the full width at half-maximum of
the \civ emission line, can be overestimated by a factor of 5 at large
blueshifts. A larger sample of quasar spectra with both \civ and H$\beta$, 
or H$\alpha$, emission lines will allow quantitative corrections to \civ-based black hole masses as a function of blueshift to be
derived. We find that quasars with large \civ blueshifts possess high
Eddington luminosity ratios and that the fraction of high-blueshift
quasars in a flux-limited sample is enhanced by a factor of
approximately 4 relative to a sample limited by black hole mass.

@@

@@

Recent investigations also include \citet{Meyer2019}.

@@

\subsection{Multi-wavelength properties}
MIR \\
Radio \\
{\bf FROM ROSS ET AL 2018!!!!} 
While previous efforts have used the 1-year baseline of the WISE mission to identify
changing-look quasars \citep[e.g.,][]{Assef2018, Stern2018}, our
investigation is the first to extend this selection to the infrared
using NEOWISE-R mission data. We have identified a sample of Sloan
Digital Sky Survey (SDSS) quasars that show significant changes in
their IR flux over the course of a few years. Importantly, our IR
light curves enable us to set limits on SED changes due to
obscuration.

We use data from the
beginning of the WISE mission \citep[2010 January; ][]{Wright2010}
through the thrid-year of NEOWISE-R operations \citep[2016 December;
][]{Mainzer2011}. The WISE scan pattern leads to coverage of the
full-sky approximately once every six months (a ``sky pass''), but the
satellite was placed in hibernation in 2011 February and then
reactivated in 2013 October. Hence, our light curves have a cadence of
6 months with a 32 month sampling gap.

The W1/W2 light curves for $\sim$200,000 SDSS and BOSS spectroscopic
quasars were obtained by performing forced photometry at the locations
of DECam-detected optical sources \citep{Lang2014, Meisner2017a,
Meisner2017b}. This forced photometry was performed on time-resolved
coadds \citep{Lang2014}, each of which represents a stack of $\sim$12
exposures. The coaddition removes the possibility of probing
variability on $\lesssim$1 day time scales, but pushes $\approx$1.4
magnitudes deeper than individual exposures while removing virtually
all single-exposure artifacts (e.g. cosmic rays and satellites).

Approximately $\sim$30,000 of the SDSS/BOSS quasars with W1/W2
light-curves available are `IR-bright', in that they are above both
the W1 and W2 single exposure thresholds and therefore detected at
very high significance in the coadds. For this ensemble of objects,
the typical variation in each quasar's measured (W1-W2) color is 0.06
magnitudes.  This includes statistical and systematic errors which are
expected to contribute variations at the few hundredths of a magnitude
level. The typical measured single-band scatter is 0.07 magnitudes in
each of W1 and W2.

### 2019-11-07 tex/other_tex/201909/CIV_notes_20190919.tex
CIV tex/ tidy up

%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
%%
%%
%%   SECTION 1  SECTION 1  SECTION 1  SECTION 1  SECTION 1  SECTION 1  
%%   SECTION 1  SECTION 1  SECTION 1  SECTION 1  SECTION 1  SECTION 1  
%%   SECTION 1  SECTION 1  SECTION 1  SECTION 1  SECTION 1  SECTION 1  
%%
%%
%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
\section{Introduction}
Luminous AGN, i.e. quasars, are now seen to significantly vary their energy output on timescales of weeks to months. 
This observational fact, and the subsequent mismatch in the expected timescale, the ``viscous'' timescale, 
which for a $\approx$10$^{7}$ M$_{\odot}$ is $\sim$hundreds of years, was noted over 30 years ago \citep[e.g.][]{Alloin1985}. 
However, with new photometric light-curve and repeat spectroscopic data, the desire for a deeper understanding 
of AGN accretion disk physics  has been re-established \citep[e.g.][]{Lawrence2018, Antonucci2018}.

Samples of over 100 ``Changing Look'' quasars (CLQs) or ``Changing State'' quasars (CSQs) have now been 
assembled \citep[e.g.][]{MacLeod2019, Graham2019}. The community uses both these
terms as a cover for the underlying physics. For sake of argument, ``Changing Look'' quasars can be 
thought of as the extension of ``regular'' quasar variability \citep[e.g.][]{MacLeod2012} whereas 
the ``Changing State'' quasars (CSQs) have a `state-transition' similar to that in Galactic X-ray binaries
\citep[e.g][]{NodaDone2018, Ruan2019}. 
%
These CLQs have primarily been defined according to their Balmer emission line properties with 
particular attention paid to the H$\beta$ emission line, usually observed from optical spectroscopy. 
As such, current CLQ studies have been at redshifts $z<1$.

While there have been a slew of studies on triply ionized carbon, i.e \civ, broad absorption line quasars
\citep[BAL QSOs; see e.g. Table 1][]{Hemler2019}, dramatic changes in the 
broad {\it emission} line (BEL) of \civ, and indeed, \ciii have not to this point been seen. 
%%

Recombination (e.g. H, He) vs. collisionally excited lines (\mgii, \civ).

Here, we report on three objects 
SDSS J120544.7+342252.4  (hereafter J1205+3422), 
SDSS J163852.93+282707.7 (hereafter J1638+2827) and
SDSS J222818.76+220102.9 (hereafter J2228+2201)  
which show dramatic changes in the \civ broad emission line
properties, as well as in the underlying continuum. We claim these are
the first examples of ``Changing Look Quasars'' at high ($z>1$)
redshift and for emission lines with high ionization potentials
(I.P.'s $>$13.6 eV).

For J1638+2827, over the course of 1279 days observed, 400 days in the rest-frame, the  broad \civ and \ciii BEL start to fade.  
For J2228+2201, over the course of 771 days observed, 240 days in the rest-frame, broad \civ and \ciii BELs both emerge and the 
standard UV/blue continuum slope increases in flux. 
the UV/blue continuum diminishes and the shape of \lya changes.

In this paper we use the wavelengths of 1548.2 and 1550.8 \AA for the \civ doublet
%Example of how to reference these results:
using the values from the National Institute of Standards and Technology (NIST) Atomic Spectra Database 
\citep{Kramida2018}. 
% A., Ralchenko, Yu., Reader, J., and NIST ASD Team (2018). NIST Atomic Spectra Database (ver. 5.6.1), [Online]. Available: https://physics.nist.gov/asd [2019, September 17]. National Institute of Standards and Technology, Gaithersburg, MD. DOI: https://doi.org/10.18434/T4W30F

%The singly ionized hydrogen atom H+ is referred to as HII, doubly ionized oxygen O++ is called OIII, etc.
%11.3 eV is the energy needed for C I to get rid of one electron, and become singly-ionised C II”
%“24.4 eV is energy needed for C I to get rid of two electrons, and become doubly-ionised C III”
%% https://en.wikipedia.org/wiki/Ionization_energies_of_the_elements_(data_page)
Using the \href{https://physics.nist.gov/PhysRefData/ASD/ionEnergy.html}{NIST Atomic Spectra Database Ionization Energies Form}
for ionisation energies, we note 47.89 eV  (3.519 Ry) is the energy required to for neutral C to dislodge three electrons and become triply--ionised \civ, 
and where 64.49 eV (4.74 Ry) is the energy needed to ionize \civ itself.

@@

%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
%%
%%   SECTION 2   SECTION 2   SECTION 2   SECTION 2   SECTION 2   SECTION 2  
%%   SECTION 2   SECTION 2   SECTION 2   SECTION 2   SECTION 2   SECTION 2  
%%   SECTION 2   SECTION 2   SECTION 2   SECTION 2   SECTION 2   SECTION 2  
%%
%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
\section{Data}
%\subsection{Selection/Identification}
%\subsection{SDSS spectra}
Lorem ipsum dolor sit amet, consectetur adipiscing elit. Aliquam porta
sodales est, vel cursus risus porta non. Vivamus vel pretium
velit. Sed fringilla suscipit felis, nec iaculis lacus convallis
ac. Fusce pellentesque condimentum dolor, quis vehicula tortor
hendrerit sed. Class aptent taciti sociosqu ad litora torquent per
conubia nostra, per inceptos himenaeos. Etiam interdum tristique diam
eu blandit. Donec in lacinia libero.

@@

Double Spectrograph (DBSP) is a low-to-medium resolution ($R\sim$1,000
to 10,000) grating instrument for the Palomar 200-inch telescope
Cassegrain focus that uses a dichroic (at, e.g., 5200\AA\ ) to split
light into simultaneously observed separate red and blue channels.

The Low Resolution Imaging Spectrometer (LRIS) is a visible-wavelength
imaging and spectroscopy instrument commissioned in 1993 and operating
at the Cassegrain focus of 10-meter Keck I telescope.

@@

%%\newpage
%% For the MNRAS Letter, not sure this can take up a full page...
\begin{figure}
  \centering
  \includegraphics[width=8.7cm, trim=0.2cm 0.2cm 0.2cm 0.2cm, clip]
  {../plots/spectral/The_3_CIV_CLQs_20190917.pdf}
% {figures/The_3_CIV_CLQs_20190917.pdf}
   \vspace{-12pt}
  \caption[]{The threes high-$z$ CLQ quasars; 
SDSS J1205+3422 (top), 
SDSS J1638+2827 (middle), 
SDSS J2228+2201 (bottom). 
%A quasar at $z = 2.2$ with the two spectra showing CIV and CIII] fading.
}
  \label{fig:civ_clqs}
\end{figure}
%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
%%
%%   SECTION 3   SECTION 3   SECTION 3   SECTION 3   SECTION 3   SECTION 3  
%%   SECTION 3   SECTION 3   SECTION 3   SECTION 3   SECTION 3   SECTION 3  
%%   SECTION 3   SECTION 3   SECTION 3   SECTION 3   SECTION 3   SECTION 3  
%%
%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
\section{Results}
Figure~\ref{fig:civ_clqs} presents the threes high-$z$ CLQ quasars. 
Nunc semper quam et leo interdum vulputate eu quis magna. Sed nec arcu
at orci egestas convallis. Aenean quam velit, aliquam vitae viverra
in, elementum vel elit. Nunc suscipit aliquet sapien a suscipit. Cras
nulla ipsum, posuere eu fringilla sit amet, dapibus ultricies
nulla. Nullam eu augue id purus mollis dignissim sed et
libero. Phasellus eget justo sed neque pellentesque egestas nec id
arcu. Donec facilisis pulvinar sapien et fringilla. Suspendisse
vestibulum rhoncus sapien id laoreet. Morbi et orci vitae tortor
imperdiet imperdiet. In hac habitasse platea dictumst. Vivamus vel
neque id mi ultrices tristique. Integer quam libero, ornare vel
gravida in, feugiat a ante. Nam dapibus, tellus vitae pellentesque
cursus, dui nisl egestas augue, non fermentum nisl est nec
nisi. Vestibulum nec mi justo, eget dapibus velit.

>>>>

%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
%%
%%
%%   SECTION 1  SECTION 1  SECTION 1  SECTION 1  SECTION 1  SECTION 1  
%%   SECTION 1  SECTION 1  SECTION 1  SECTION 1  SECTION 1  SECTION 1  
%%   SECTION 1  SECTION 1  SECTION 1  SECTION 1  SECTION 1  SECTION 1  
%%
%%
%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
\section{Introduction}
Luminous AGN, i.e. quasars, are now seen to significantly vary their
energy output on timescales of weeks to months.  This observation, and
the subsequent mismatch in the expected ``viscous'' timescale, which
for a $\approx$10$^{7}$ M$_{\odot}$ is $\sim$hundreds of years, was
noted over 30 years ago \citep[e.g.][]{Alloin1985}. However, with new
photometric light-curve and repeat spectroscopic data, the desire for
a deeper understanding of AGN accretion disk physics has been recently
re-invigorated the field \citep[e.g.][]{Lawrence2018, Antonucci2018}.

Samples of over 100 ``Changing Look'' quasars (CLQs) or ``Changing State'' quasars (CSQs) have now been 
assembled \citep[e.g.][]{MacLeod2019, Graham2019}. The community uses both these
terms as a cover for the underlying physics. For sake of argument, ``Changing Look'' quasars can be 
thought of as the extension of ``regular'' quasar variability \citep[e.g.][]{MacLeod2012} whereas 
the ``Changing State'' quasars (CSQs) have a `state-transition' similar to that in Galactic X-ray binaries
\citep[e.g][]{NodaDone2018, Ruan2019}. 
%
These CLQs have primarily been defined according to the (recombination) Balmer emission line properties with 
particular attention paid to the H$\beta$ emission line, usually observed from optical spectroscopy. 
As such, current CLQ studies have been at redshifts $z<1$.

While there have been a slew of studies on triply ionized carbon, i.e
\civ, these have tended to focus on broad absorption line quasars
\citep[BAL QSOs; see e.g. Table 1][]{Hemler2019} or the Baldwin Effect
\citep[BEff; e.g. ][]{Baldwin1977, Bian2012, Jensen2016,
Hamann2017}\footnote{As noted in \citet{Rakic2017}, two different
types of Baldwin effect are present in the literature: the {\it
global} (or {\it ensemble}) Baldwin Effect, which is an anti-correlation
between the EW of the emission line and the underlying continuum
luminosity of {\it single-epoch} observations of a {\it large number}
of AGN and second, the {\it intrinsic} Baldwin effect, the same anti-correlation
but in an {\it individual, variable} AGN \citep{PoggePeterson1992}.}.
%%
Dramatic changes in the collisionally excited  broad {\it emission} line (BEL) 
of \civ (and indeed \ciii) have not to this point been seen.

Here, we report on three quasars  
%SDSS J120544.7+342252.4  (hereafter J1205+3422), 
%SDSS J163852.93+282707.7 (hereafter J1638+2827) and
%SDSS J222818.76+220102.9 (hereafter J2228+2201)  
which show dramatic changes in their \civ\ and \ciii broad emission line
properties as well as in the underlying continuum. We claim these are
the first examples of ``Changing Look Quasars'' at high ($z>1$)
redshift. Moreover, these are cases for dramatic changes of 
ions with high ionization potentials (I.P.'s $>$2 Rydberg).

%%
In this paper we use the wavelengths of 1548.202 and 1550.774 \AA\ for the \civ doublet
%Example of how to reference these results:
using the values from the National Institute of Standards and Technology (NIST) Atomic Spectra Database 
\citep{Kramida2018}. 
% A., Ralchenko, Yu., Reader, J., and NIST ASD Team (2018). NIST Atomic Spectra Database (ver. 5.6.1), [Online]. Available: https://physics.nist.gov/asd [2019, September 17]. National Institute of Standards and Technology, Gaithersburg, MD. DOI: https://doi.org/10.18434/T4W30F

%The singly ionized hydrogen atom H+ is referred to as HII, doubly ionized oxygen O++ is called OIII, etc.

%“24.4 eV is energy needed for C I to get rid of two electrons, and become doubly-ionised C III”
%% https://en.wikipedia.org/wiki/Ionization_energies_of_the_elements_(data_page)
The ground state of carbon is 1$s^2$ 2$s^2$ 2$p^2$.
Using the \href{https://physics.nist.gov/PhysRefData/ASD/ionEnergy.html}{NIST Atomic Spectra Database Ionization Energies Form}
for ionisation energies, we see 
11.3 eV is the energy needed for C I to dislodge one electron and become singly-ionised C II; 
24.4 eV is energy needed for singly-ionised C II to dislodge an additional electron, and become doubly-ionised C III, 
and 47.89 eV  (3.519 Ry) is required for doubly-ionised C III  become triply--ionised \civ. 
64.49 eV (4.74 Ry) is the energy needed to ionize \civ itself.

The 1548.202 	and 1550.774 \AA\ emission doublet is created by the 
2$p$ $^{2}P_{0}$ $---$  2$s$ $^{2}S$ transition with 
energies 64,484 cm$^{-1}$ and 64591 cm$^{-1}$ 
\citep[e.g.][]{Moore1993}.

Ground  Shells:  1$s^{2}$2$s$. 
Ground  Level: $^{2}S_{1/2}$. 
Ionized  Level: 1$s^{2}$ $^{1}S_{0}$.

@@

%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
%%
%%   SECTION 2   SECTION 2   SECTION 2   SECTION 2   SECTION 2   SECTION 2  
%%   SECTION 2   SECTION 2   SECTION 2   SECTION 2   SECTION 2   SECTION 2  
%%   SECTION 2   SECTION 2   SECTION 2   SECTION 2   SECTION 2   SECTION 2  
%%
%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
\section{Data}
%\subsection{Selection/Identification}
\subsection{Spectra}
An overview of our spectroscopic observations is given in Table~\ref{tab:obs_notes}. 
The spectra are from the SDSS \citep{Stoughton2002, DR7, Schneider2010},  
the SDSS-III Baryon Oscillation Spectroscopic Survey \citep[BOSS][]{Eisenstein2011, Dawson2013, Smee2013, Alam2015, Paris2017} 
and the SDSS-IV  Extended Baryon Oscillation Spectroscopic Survey \citep[eBOSS; ][]{Dawson2016, Abolfathi2018}. 
These quasars were targetted via a range of techniques and algorithms \citep[][]{Richards2002, Ross2012, 
Myers2015}.  
These data are supplemented by spectra from 
the Low Resolution Imaging Spectrometer (LRIS) on the 10m Keck {\sc I} telescope \citep{Oke1995}. 
%% The Keck Low Resolution Imaging Spectrometer", Oke, J.B., et al.. 1995, PASP, 107, 375
and the Double Spectrograph (DBSP) instrument on the Palomar {\it Hale} 5m telescope.

\subsection{Line Properties}. 
We use the measured quasar emission line properties from \citet{Shen2011} and \citet{Hamann2017}. 
\citet{Hamann2017} in particular investigate in robust detail the UV continuum and the \civ (and \nv $\lambda$ $\lambda$1238, 1242) emission lines in 
over 200,000 quasars in BOSS DR12Q \citep{Paris2017}\footnote{This emission-line catalog 
can be downloaded from \href{https://datadryad.org/stash/dataset/doi:10.6086/D1H59V}{here}.}
The quasar redshift are limited to the range 1.53 ≤ ze ≤ 5.0 so that C IV and the adjacent continuum are covered by BOSS. 
These measurements provide line profile information and N V/C IV flux ratios

@@

@@

%%\newpage
%% For the MNRAS Letter, not sure this can take up a full page...
\begin{figure}
  \centering
  \includegraphics[width=8.7cm, trim=0.2cm 0.2cm 0.2cm 0.2cm, clip]
  {../plots/spectral/The_3_CIV_CLQs_20190917.pdf}
% {figures/The_3_CIV_CLQs_20190917.pdf}
   \vspace{-12pt}
  \caption[]{The threes high-$z$ CLQ quasars; 
SDSS J1205+3422 (top), 
SDSS J1638+2827 (middle), 
SDSS J2228+2201 (bottom). 
%A quasar at $z = 2.2$ with the two spectra showing CIV and CIII] fading.
}
  \label{fig:civ_clqs}
\end{figure}

\begin{figure*}
  \centering
  %% trim=l b r t
  \includegraphics[width=16.7cm, trim=0.0cm 0.1cm 0.2cm 0.1cm, clip]
  % {../plots/spectral/The_3_CIV_CLQs_20190917.pdf}
  {../plots/perObject/J1205+3422_landscape_20190920.png}
  \includegraphics[width=16.7cm, trim=0.0cm 0.1cm 0.2cm 0.1cm, clip]
  {../plots/perObject/J1638+2827_landscape_20190920.png}
  \includegraphics[width=16.7cm, trim=0.0cm 0.1cm 0.2cm 0.1cm, clip]
  {../plots/perObject/J2228+2201_landscape_20190920.png}
  \vspace{-12pt}
  \caption[]{The threes high-$z$ CLQ quasars; 
    SDSS J1205+3422 (top), 
    SDSS J1638+2827 (middle), 
    SDSS J2228+2201 (bottom). 
    % A quasar at $z = 2.2$ with the two spectra showing CIV and CIII] fading.
  }
  \label{fig:civ_clqs2}
\end{figure*}

%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
%%
%%   SECTION 3   SECTION 3   SECTION 3   SECTION 3   SECTION 3   SECTION 3  
%%   SECTION 3   SECTION 3   SECTION 3   SECTION 3   SECTION 3   SECTION 3  
%%   SECTION 3   SECTION 3   SECTION 3   SECTION 3   SECTION 3   SECTION 3  
%%
%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
\section{Results}
Figure~\ref{fig:civ_clqs} presents the threes high-$z$ CLQ quasars. 
%%
%%
For J1638+2827, over the course of 1279 days observed, 400 days in the rest-frame, the  broad \civ and \ciii BEL start to fade.  
For J2228+2201, over the course of 771 days observed, 240 days in the rest-frame, broad \civ and \ciii BELs both emerge and the 
standard UV/blue continuum slope increases in flux. 
the UV/blue continuum diminishes and the shape of \lya changes.
